%% For Use With NIH Biosketch LaTeX Class
%% Added to RMarkdown by Tyson S. Barrett, PhD

% Document class and options
\documentclass{nihbiosketch}
\usepackage{natbib}
\usepackage{bibentry}
\bibliographystyle{apalike}
\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Pandoc header




\name{Frederick J. Boehm}
\eracommons{fjboehm}
\position{Postdoc}


\begin{document}



  \nobibliography{boehm.bib}


  \begin{education}
      University of Wisconsin-Madison & B.S. & 5/2001 & Chemistry \\
      University of Wisconsin-Madison & M.D. & 8/2007 & Medicine \\
      University of Wisconsin-Madison & M.S. & 8/2007 & Population health sciences \\
      University of Wisconsin-Madison & Ph.D. & 5/2019 & Statistics \\
    \end{education}



\hypertarget{personal-statement}{%
\section*{Personal Statement}\label{personal-statement}}
\addcontentsline{toc}{section}{Personal Statement}

Your statement about your qualifications for the proposal goes here.
Include up-to-four citations related to the statement (either using the
\texttt{make\_numbered\_citations()} function as shown below with the
appropriate keys from the \texttt{.bib} file or manually entered). This
can often include any previous products from collaborations between the
research team that is relevant to the current proposal. Ultimately, this
is a space to show that you are competent capable of completing the
proposed project. Feel free to erase all of this filler text.

\begin{enumerate}
  \item \bibentry{boehm2019testing}
  \item \bibentry{boehm2019qtl2pleio}
  \item \bibentry{kemis2019genetic}
\end{enumerate}

\hypertarget{positions-and-honors}{%
\section*{Positions and Honors}\label{positions-and-honors}}
\addcontentsline{toc}{section}{Positions and Honors}

\hypertarget{positions-and-employment}{%
\subsection*{Positions and Employment}\label{positions-and-employment}}
\addcontentsline{toc}{subsection}{Positions and Employment}

\begin{datetbl}
2019-- & Postdoctoral associate, Department of Microbiology and Physiological Systems, University of Massachusetts Medical School, Worcester, Massachusetts \\
\end{datetbl}

\hypertarget{other-experience-and-professional-memberships}{%
\subsection*{Other Experience and Professional
Memberships}\label{other-experience-and-professional-memberships}}
\addcontentsline{toc}{subsection}{Other Experience and Professional
Memberships}

\begin{datetbl}
2000-- & Member, Gerontological Society of America \\
2000-- & Member, American Psychological Association \\
\end{datetbl}

\hypertarget{honors}{%
\subsection*{Honors}\label{honors}}
\addcontentsline{toc}{subsection}{Honors}

\begin{datetbl}
2018 & Best poster award, International Mammalian Genome Conference \\
2018 & Conference travel scholarship, International Mammalian Genome Conference \\
2013 & New Arts Venture Challenge award, University of Wisconsin-Madison \\
2013 & Integrating research ethics and scholarship fellowship, University of Wisconsin-Madison \\
2006 & Medical student research training fellowship, Howard Hughes Medical Institute \\
2001 & University Bookstore award for outstanding undergraduate thesis, University of Wisconsin-Madison \\
2001 & Graduate research fellowship, National Science Foundation \\
1996 & Wisconsin academic excellence scholarship, University of Wisconsin-Madison \\
\end{datetbl}

\hypertarget{contribution-to-science}{%
\section*{Contribution to Science}\label{contribution-to-science}}
\addcontentsline{toc}{section}{Contribution to Science}

\begin{enumerate}

\item Paragraph of contribution number 1. This should include a narrative about one of your main research lines. Below, cite up to four publications stemming from this contribution. Feel free to erase all of this filler text.

\begin{enumerate}
  \item \bibentry{RCoreTeam}
  \item \bibentry{RStudio}
  \item \bibentry{biosketchr}
  \item \bibentry{nihbiosketch}
\end{enumerate}


\item Paragraph of contribution number 2. This should include a narrative about one of your main research lines. Below, cite up to four publications stemming from this contribution. Feel free to erase all of this filler text.

\begin{enumerate}
  \item \bibentry{RCoreTeam}
  \item \bibentry{RStudio}
  \item \bibentry{biosketchr}
  \item \bibentry{nihbiosketch}
\end{enumerate}

\end{enumerate}



  \subsection*{Complete List of Published Work in MyBibliography:} 
  \url{url}




\end{document}
